LabMate: supporting types for MATLAB

### 2024-04-10 writing/IMEKOWC2024/LabMate/paper.tex
[ writing ] abstract and (commented out) keywords

\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO: #1}}}

@@

\begin{abstract}
  TODO
\end{abstract}
\begin{keywords}
  TODO
\end{keywords}

>>>>

\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO: #1}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{abstract}
  Many computations in science and engineering are implemented in the
  programming language MATLAB. However the high-level meaning of such
  MATLAB programs stay informal, which can lead to implementation
  errors and bugs, for example relating to incompatible units of
  measure for quantities, or incompatible sizes of matrices at
  runtime. We are in the process of developing LabMate, which is a
  tool for reifying current informal programmer practices into a
  language of formal comments. These comments are ignored by MATLAB,
  but acted on and checked by LabMate. We outline the design
  principles behind LabMate, our current progress, and our future
  plans.
\end{abstract}
%\begin{keywords}
%  MATLAB, software correctness, dimensional consistency, type theory
%\end{keywords}
